Actuator line modeling of vertical-axis turbines

### 2016-05-02 paper.tex
Note that the spanwise flow is neglected

Assuming unsteady effects can be appropriately modeled, the blade element lift
and drag forces are calculated as
\begin{equation}
    F_l = \frac{1}{2} \rho A_\mathrm{elem} C_l |\vec{U}_\mathrm{rel}|^2,
\end{equation}
and
\begin{equation}
    F_d = \frac{1}{2} \rho A_\mathrm{elem} C_d |\vec{U}_\mathrm{rel}|^2,
\end{equation}
where $\rho$ is the fluid density, $A_\mathrm{elem}$ is the blade element
planform area (span $\times$ chord), $\vec{U}_\mathrm{rel}$ is the local
relative velocity, and $C_l$ and $C_d$ are the sectional lift and drag
coefficients, linearly interpolated from a table per the local angle of attack.
The forces are then projected onto the rotor coordinate system to calculate
torque, overall drag, etc. Forces from the turbine shaft and blade support
struts are computed in a similar way. After the force on the actuator lines from
the flow is computed, it is then added to the Navier--Stokes equations as a body
force or momentum source (per unit density, assuming incompressible flow):
\begin{equation}
    \frac{\mathrm{D} \vec{u}}{\mathrm{D} t} = - \frac{1}{\rho} \nabla p + \nu
    \nabla^2 \vec{u} + F_\mathrm{turbine}.
\end{equation}

>>>>

Assuming unsteady effects can be appropriately modeled, the blade element lift
and drag forces are calculated as
\begin{equation}
    F_l = \frac{1}{2} \rho A_\mathrm{elem} C_l |\vec{U}_\mathrm{rel}|^2,
\end{equation}
and
\begin{equation}
    F_d = \frac{1}{2} \rho A_\mathrm{elem} C_d |\vec{U}_\mathrm{rel}|^2,
\end{equation}
where $\rho$ is the fluid density, $A_\mathrm{elem}$ is the blade element
planform area (span $\times$ chord), $\vec{U}_\mathrm{rel}$ is the local
relative velocity projected onto the plane of the element profile cross-section
(i.e., the spanwise component is neglected), and $C_l$ and $C_d$ are the
sectional lift and drag coefficients, linearly interpolated from a table per the
local angle of attack. The forces are then projected onto the rotor coordinate
system to calculate torque, overall drag, etc. Forces from the turbine shaft and
blade support struts are computed in a similar way. After the force on the
actuator lines from the flow is computed, it is then added to the Navier--Stokes
equations as a body force or momentum source (per unit density, assuming
incompressible flow):
\begin{equation}
    \frac{\mathrm{D} \vec{u}}{\mathrm{D} t} = - \frac{1}{\rho} \nabla p + \nu
    \nabla^2 \vec{u} + F_\mathrm{turbine}.
\end{equation}
